---
title: "Infected Shoulders: Analysis Pipeline"
author: "Enterprise Analytics"
date: "`r paste0('Last Updated: ', format(Sys.time(), '%d %B, %Y')) `"
keywords: 
  - Heart and Vascular
  - population health
  - Geo Data
output: 
  eatemplates::ea_report:
    analyst: 
    - "P. Walker"
    email: "philip.walker@conehealth.com"
    draft: false
    code_folding: "show" # one of "show", "hide", or "none"
    code_download: FALSE # TRUE to allow the Rmd to be downloaded or FALSE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.align = 'center',out.width="80%")
library(tidyverse)
# library(eaverse)
library(eastyle)
library(eadb)
library(gt)
library(DBI)
library(glue)
library(lubridate)
library(openxlsx)
# To Turn off Scientific Notation Use this.
options(scipen = 999)

InfecDX <- readxl::read_excel(here::here("notes", "PSI_Appendix_F.xlsx"), sheet = "dx_only") %>% 
  pull(DX_code)


```

# Build Procedue List
```{r}

keywords <- paste(c(
  # from feedback on 11/10/2020
  "SHOULDER ARTHROPLASTY", "TOTAL SHOULDER", "SHOULDER REPLACEMENT", "ARTHROPLASTY", "SHOULDER REVERSE REPLACEMENT", "SHOULDER REVISION",
  # from feedback on 1/5/2021
  "IRRIGATION AND DEBRIDEMENT", "IRRIGATION & DEBRIDEMENT", "ARTHROSCOPIC", "ARTHROSCOPY","INCISION AND DRAINAGE", "INCISION & DRAINAGE",
  # from feedback on 1/15/2021
  "TOTAL SHOULDER", "SHOULDER ARTHROPLASTY", "SHOULDER REPLACEMENT", "SHOULDER SCOPE", "SHOULDER WASHOUTS", "SHOULDER IRRIGATION & DEBRIDEMENT"
  ),
  collapse = "|")

```

# Pull Historical Surgery Data

```{r}


shoulders_Output <- 
  submit_edw_query(
    template = "
      SELECT bbb.[PatientEncounterID], a.[LogID],[LogNM],[SurgeryDTS] ,[CaseClassDSC], a.PatientID 
    ,c.MRN, [PatientTypeDSC] ,[TotalTimeNeededMinutesNBR] ,[RoomID],[StatusDSC] ,[ServiceDSC] 
    ,[ScheduleStartDTS] ,[ProcessedByEndOfDayFLG] ,[CaseRequestID],[InpatientDataID] ,[ProcedureLevelDSC] 
    ,[TimingEventStatusDSC] ,a.[CaseID],[EmergencyStatusStoredFLG],[UseProcedureFLG]  ,[PrimaryPhysicianID]
    ,d.[ProviderNM] ,b.[AsOrderedProcedureNM], b.[ProcedureID], b.[BodySectionDSC], b.[BodyRegionDSC] 
	  ,bb.[DepartmentDSC] ,bb.[ExternalNM] ,bb.[RevenueLocationNM]
  FROM [Epic].[Surgery].[SurgicalLog] a
    left join [Epic].[Surgery].[LogAllProcedure] b on a.logid = b.logid
	  left join [Epic].[Surgery].[AdmissionLink] bbb on a.logid = bbb.logid
    left join epic.patient.patient c on a.patientid = c.patientid
	  left join [Epic].[Reference].[Resource1] d on a.primaryphysicianid = d.[ProviderID]
	  left join [Epic].[Surgery].[Location] aa on a.[LocationID] = aa.[LocationID]
	  left join [Epic].[Reference].[Department] bb on aa.[OperatingRoomDepartmentID] = bb.[DepartmentID]
  where servicedsc in ('Orthopedics')
    and surgerydts >= '2014-01-01'
    and b.BodyRegionDSC in ('Shoulder')
  order by surgerydts",
    edw_dsn = "MCCBIEDW1",
    show_query = T
)


shoulders_Output <-
  shoulders_Output %>% 
  mutate(AsOrderedProcedureNM = toupper(trimws(iconv(AsOrderedProcedureNM, "UTF-8", "UTF-8",sub=''))),
         InProcedures = str_detect(toupper(trimws(AsOrderedProcedureNM)), keywords),
         DT = as.Date(SurgeryDTS)) %>% 
  ungroup()


save(shoulders_Output, file = here::here("data-raw", "shoulders_Output.rda"))  


MaxDT <- max(shoulders_Output$DT, na.rm=T)
MinDT <- min(shoulders_Output$DT, na.rm=T)

```

```{r}
ProcedID <-
  shoulders_Output %>% 
  filter(InProcedures == T) %>% 
  distinct(ProcedureID) %>% 
  pull(ProcedureID)
  

shoulders_Output <-
  shoulders_Output %>% 
  mutate(InProcID = ifelse(ProcedureID %in% ProcedID, T,F),
         InProcedures = ifelse(is.na(InProcedures), F, InProcedures),
         Proced_Match = InProcID + InProcedures)



```



## Procedure Review
```{r}

shoulders_Output %>% 
  count(Proced_Match, sort=T)

IncludedProc <-
  shoulders_Output %>% 
  filter(Proced_Match != 0) %>% 
  count(ProcedureID, AsOrderedProcedureNM) %>% 
  group_by(ProcedureID) %>% 
  mutate(TotalByPID = sum(n)) %>% 
  ungroup() %>% 
  arrange(desc(TotalByPID), desc(n)) %>% 
  # head(6) %>%
  ungroup()


```



# Pull Infections Dx
Per Heather (2021.01.15): "They do want infections up to 6 months post-surgery and a time span of the last 5 years from 2019"

```{r}
pat <- 
  shoulders_Output %>% 
  distinct(PatientID) %>% 
  pull(PatientID)

# DxList <- InfecDX
```


```{r}

EDW = DBI::dbConnect(odbc::odbc(), dsn = "MCCBIEDW1")

infec_sql <- glue_sql("
SELECT [PatientEncounterID] ,[LineNBR] ,[PatientID] ,[PatientEncounterDateRealNBR]
      ,[ContactDTS] ,a.[DiagnosisID] ,a.[DiagnosisNM], CurrentICD10ListTXT,[DiagnosisDSC],[PrimaryDiagnosisFLG] ,[UpdateDTS]
  FROM [Epic].[Encounter].[PatientEncounterDiagnosis] a
  left join [Epic].[Reference].[Diagnosis] b on a.DiagnosisID = b.DiagnosisID
  where a.DiagnosisID in (select DiagnosisID FROM [Epic].[Reference].[Diagnosis] 
                    				where (CurrentICD10ListTXT like ('%T81.%') or CurrentICD10ListTXT like ('%T84.%')))
  and contactdts >= '2014-01-01'
  and patientid in ({pat*})
", 

.con = EDW)

infec_ <- dbSendQuery(EDW, infec_sql)
infec_DX_Output <- dbFetch(infec_)


infect_clean_DX <-
  infec_DX_Output %>% 
  mutate(DT = as.Date(ContactDTS)) %>%
  group_by(PatientID) %>% 
  distinct(PatientID, infectDT = DT) %>% 
  ungroup() %>% 
  arrange(PatientID) %>% 
  group_by(PatientID) %>% 
  nest(data = c(infectDT)) %>% 
  mutate(DxCount = lengths(data))

```

# Join surgeries to infections

```{r}

shoul_map_infections <-
  shoulders_Output %>% 
  mutate(DT = as.Date(SurgeryDTS),
         DT_wk = lubridate::floor_date(DT, "week"),
         DT_infecTest = DT %m+% months(6)) %>% 
  select(PatientID, DT, DT_infecTest) %>% 
  left_join(., infect_clean_DX,
            by = c("PatientID")) %>% 
  ungroup() %>% 
  filter(!is.na(DxCount)) %>% 
  unnest(cols = c(data)) %>%
  mutate(InfecInterval = interval(DT, DT_infecTest),
         WithinInfecDT = infectDT %within% InfecInterval) %>% 
  group_by(PatientID, DT) %>% 
  mutate(CountInfec = sum(WithinInfecDT)) %>%
  ungroup() %>% 
  filter(WithinInfecDT == T) %>% 
  arrange(PatientID, DT, infectDT) %>% 
  group_by(PatientID, DT, CountInfec) %>% 
  summarise(InfectDt_Flagged = toString(infectDT))


shoul_clean <-
  shoulders_Output %>% 
  mutate(DT = as.Date(SurgeryDTS),
         DT_wk = lubridate::floor_date(DT, "week"),
         DT_infecTest = DT %m+% months(6)) %>% 
  left_join(., shoul_map_infections) %>% 
  mutate(CountInfec = ifelse(is.na(CountInfec), 0, CountInfec),
         Proced_Match = ifelse(Proced_Match == 0, F ,T)) %>%
  select(-InProcID, -InProcedures, -RoomID, -TotalTimeNeededMinutesNBR, -ProcessedByEndOfDayFLG, -CaseRequestID, -InpatientDataID,
         -LogNM,-CaseRequestID, -CaseID, -PrimaryPhysicianID, -ExternalNM, -EmergencyStatusStoredFLG, -UseProcedureFLG,
         -DT_infecTest, -BodySectionDSC, -BodyRegionDSC, -ServiceDSC, -SurgeryDTS) %>% 
  ungroup()

  
save(shoul_clean, file = here::here("data-raw", "shoul_clean.rda"))  

```



# Dataset for Heather

```{r}

Shld_Out <-
  shoul_clean %>% 
  filter(StatusDSC == "Posted",
         TimingEventStatusDSC == "Completed",
         !is.na(CaseClassDSC),
         !is.na(DepartmentDSC),
         Proced_Match == T) %>% 
  ungroup() %>% 
  mutate(Had_Infection_Dx = ifelse(CountInfec == 0, "No", "Yes")) %>% 
  select(CaseID = LogID, ProviderNM, DepartmentDSC, SurgeryDTS = DT, CaseClassDSC, PatientTypeDSC, 
         ProcedureLevelDSC, ProcedureName = AsOrderedProcedureNM,
         Had_Infection_Dx,InfectDt_Flagged) %>% 
  mutate(ProcedureName = toupper(trimws(ProcedureName))) %>%
  ungroup() %>% 
  arrange(SurgeryDTS, CaseID)


```


Counts of Patient Type by Loc and Year

```{r}

piv_Loc_Year <-
  Shld_Out %>% 
  count(Year =lubridate::year(SurgeryDTS), PatientTypeDSC, DepartmentDSC) %>% 
  pivot_wider(names_from = Year, values_from = n) %>% 
  arrange(DepartmentDSC, PatientTypeDSC)


```

Provider List 

```{r}

ProvList <- 
  shoulders_Output %>% 
  count(PrimaryPhysicianID, ProviderNM, sort=T) %>% 
  # arrange(n) %>% 
  ungroup()

```

Infection Yearly Rate

```{r}
Inf_rate <-
  Shld_Out %>% 
  count(Year =lubridate::year(SurgeryDTS), Had_Infection_Dx) %>% 
  pivot_wider(names_from = Had_Infection_Dx, values_from = n) %>% 
  mutate(Percentage_Infec = Yes/ (Yes + No))
  
```


Plot of trends

```{r}

p1 <-
  Shld_Out %>%
  mutate(DT_wk = lubridate::floor_date(SurgeryDTS, "month")) %>% 
  count(DT_wk, CaseClassDSC, DepartmentDSC) %>% 
  ggplot(aes(DT_wk, n))+
    geom_line(color="grey")+
    geom_point(size = 0.9)+
    facet_grid(CaseClassDSC ~ DepartmentDSC)+
    theme_cone_facet()+
  labs(title = "Monthly Count of Surgeries by Location and Case Class",
       subtitle = glue::glue("For surgeries from {MinDT} - {MaxDT} "),
       y = NULL, x=NULL)+
  theme(strip.text = element_text(size =14))

  
  
```



# Write out restults to Excel for Heather


```{r write to excel}

wb <- createWorkbook()

addWorksheet(wb, sheetName = "Raw_Data")
addWorksheet(wb, sheetName = "PatientType_Year")
addWorksheet(wb, sheetName = "Procedure_List")
addWorksheet(wb, sheetName = "Provider_List")
addWorksheet(wb, sheetName = "Infections_Year")

writeDataTable(wb, sheet = 1, x = Shld_Out,
  colNames = TRUE, rowNames = F,
  tableStyle = "TableStyleLight9")

writeDataTable(wb, sheet = 2, x = piv_Loc_Year,
  colNames = TRUE, rowNames = F, xy = c("A", 1),
  tableStyle = "TableStyleLight9")

writeDataTable(wb, sheet = 3, x = IncludedProc,
  colNames = TRUE, rowNames = F,
  tableStyle = "TableStyleLight9")

writeDataTable(wb, sheet = 4, x = ProvList,
  colNames = TRUE, rowNames = F,
  tableStyle = "TableStyleLight9")

writeDataTable(wb, sheet = 5, x = Inf_rate,
  colNames = TRUE, rowNames = F,
  tableStyle = "TableStyleLight9")

print(p1)
insertPlot(wb, 1, xy = c("M", 2), width = 28, height = 15,  fileType = "png", units = "cm")

saveWorkbook(wb, file = here::here("output","Shoulder_Surgery_2014_2020.xlsx"), overwrite = TRUE)

```






